---
---
title: "Used Car Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("tidyverse")
install.packages("plotly")

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
```

#new dataset, this is mainly just sorting all the data into two categories that best fit
```{r}
cars <- read.csv('usedcars_dataset.csv')
```
#splitting dataset by less than four or greater than four because four cylinders are the most common engine
```{r}
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'three'] <- '<= four'
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'two'] <- '<= four'
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'four'] <- '<= four'
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'five'] <- '>= five'
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'six'] <- '>= five'
cars["num.of.cylinders"][cars["num.of.cylinders"] == 'eight'] <- '>= five'
```
#changed 4wd to fwd because it was a similar price 
```{r}
cars["drive.wheels"][cars["drive.wheels"] == '4wd'] <- 'fwd'
```
#these were also made by price sedan and wagon are together because those are consumer cars while hardtop convertible and hatchbacks are sportier
```{r}
cars["body.style"][cars["body.style"] == "hardtop"] <- "hatchback"
cars["body.style"][cars["body.style"] == "convertible"] <- "hatchback"
cars["body.style"][cars["body.style"] == "7"] <- "hatchback"
cars["body.style"][cars["body.style"] == "wagon"] <- "sedan"
```
#I made all the ohcs ohc because theyre basically the same thing. I made the l engine dohc because they were similar price
```{r}
cars["engine.type"][cars["engine.type"] == "l"] <- "dohc"
cars["engine.type"][cars["engine.type"] == "ohcf"] <- "ohc"
cars["engine.type"][cars["engine.type"] == "ohcv"] <- "ohc"
cars["engine.type"][cars["engine.type"] == "rotor"] <- "dohc"
```
#NA didn't like me so I just made NA t
```{r}
cars[cars == ""] <- 't'
```
```{r}
cars['num.of.doors'][cars['num.of.doors'] == 't' ] <- "two"
```
#making median and high the same category because there were so little of them
```{r}
cars['price_binned'][cars['price_binned'] == 'Median'] <- 'Mid->High'
cars['price_binned'][cars['price_binned'] == 'High'] <- 'Mid->High'
```
#making the binary more like decision tress
```{r}
cars['diesel'][cars['diesel'] == '1'] <- 'Yes'
cars['diesel'][cars['diesel'] == '0'] <- 'No'
cars['gas'][cars['gas'] == '1'] <- 'Yes'
cars['gas'][cars['gas'] == '0'] <- 'No'
```

#All my graphs to figure out my data parse
```{r}
ggplot(cars, aes(x=make)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```
```{r}
ggplot(cars, aes(x=drive.wheels)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```


```{r}
ggplot(cars, aes(x=engine.location)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```


```{r}
ggplot(cars, aes(x=num.of.cylinders)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=engine.type)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=aspiration)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=num.of.doors)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=body.style)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=fuel.system)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=price_binned)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```


```{r}
ggplot(cars, aes(x=body.style)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
ggplot(cars, aes(x=engine.type)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```

```{r}
cars['body.style'] <- replace(cars['body.style'], 'hardtop','hatchback')


```
```{r}

ggplot(cars, aes(x = factor(drive.wheels), y = price)) + 
  geom_bar(stat = "summary", fun = "mean")

``` 

```{r}
ggplot(cars, aes(x = factor(price_binned), y = price)) + 
  geom_bar(stat = "summary", fun = "mean")
```  

```{r}
ggplot(cars, aes(x=price_binned)) +
geom_bar() +
geom_text(stat='count', aes(label=..count..), vjust=-1) +
theme(axis.text.x = element_text(angle = 90))
```
```{r}
write.csv(cars, 'used_car_binary.csv')
```

data <- subset(cars, select= c(price,price_binned))
data
